% do not change these two lines (this is a hard requirement
% there is one exception: you might replace oneside by twoside in case you deliver 
% the printed version in the accordant format
\documentclass[11pt,titlepage,oneside,openany]{article}
\usepackage{times}


\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{ntheorem}

% \usepackage{paralist}
\usepackage{tabularx}

% this packaes are useful for nice algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[paper=a4paper,left=40mm,right=40mm,top=50mm,bottom=50mm]{geometry}

%Packages Max Darmstadt
\usepackage{lipsum}
\usepackage{xargs}%For todo notes
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} % Commands for more todo options
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=green,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=purple,backgroundcolor=purple!25,bordercolor=purple,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}} % usable todo commands: todo, unsure, change, info, improvement, thiswillnotshow

%Packages Nicolas Fürhaupter
\usepackage{color}

%Packages Erik Penther
\usepackage{xurl}
%\usepackage{hyperref}
%\hypersetup{hidelinks}

% well, when your work is concerned with definitions, proposition and so on, we suggest this
% feel free to add Corrolary, Theorem or whatever you need
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}


% its always useful to have some shortcuts (some are specific for algorithms
% if you do not like your formating you can change it here (instead of scanning through the whole text)
\renewcommand{\algorithmiccomment}[1]{\ensuremath{\rhd} \textit{#1}}
\def\MYCALL#1#2{{\small\textsc{#1}}(\textup{#2})}
\def\MYSET#1{\scshape{#1}}
\def\MYAND{\textbf{ and }}
\def\MYOR{\textbf{ or }}
\def\MYNOT{\textbf{ not }}
\def\MYTHROW{\textbf{ throw }}
\def\MYBREAK{\textbf{break }}
\def\MYEXCEPT#1{\scshape{#1}}
\def\MYTO{\textbf{ to }}
\def\MYNIL{\textsc{Nil}}
\def\MYUNKNOWN{ unknown }
% simple stuff (not all of this is used in this examples thesis
\def\INT{{\mathcal I}} % interpretation
\def\ONT{{\mathcal O}} % ontology
\def\SEM{{\mathcal S}} % alignment semantic
\def\ALI{{\mathcal A}} % alignment
\def\USE{{\mathcal U}} % set of unsatisfiable entities
\def\CON{{\mathcal C}} % conflict set
\def\DIA{\Delta} % diagnosis
% mups and mips
\def\MUP{{\mathcal M}} % ontology
\def\MIP{{\mathcal M}} % ontology
% distributed and local entities
\newcommand{\cc}[2]{\mathit{#1}\hspace{-1pt} \# \hspace{-1pt} \mathit{#2}}
\newcommand{\cx}[1]{\mathit{#1}}
% complex stuff
\def\MER#1#2#3#4{#1 \cup_{#3}^{#2} #4} % merged ontology
\def\MUPALL#1#2#3#4#5{\textit{MUPS}_{#1}\left(#2, #3, #4, #5\right)} % the set of all mups for some concept
\def\MIPALL#1#2{\textit{MIPS}_{#1}\left(#2\right)} % the set of all mips


\begin{document}

\pagenumbering{roman}
% lets go for the title page, something like this should be okay
\begin{titlepage}
	\vspace*{2cm}
  \begin{center}
   {\Large Outline Proposal Paper\\}
   \vspace{2cm} 
   {Team:\\}
   {\Large \textbf{MINEheim}\\}
   \vspace{1cm}
   {Data Mining 1\\}
   \vspace{2cm}
   {presented by\\
    Anna-Lena Blinken (1818326)\\
	Nicolas Hautschek (1816720)\\
	Max Darmstadt (1820000)\\
	Erik Penther (1602026)\\
	Nicolas Fürhaupter (1819446)\\
   }
   \vspace{1cm} 
   %{submitted to the\\
   % Data and Web Science Group\\
   % Prof.\ Dr.\ Right Name Here\\
   % University of Mannheim\\} \vspace{2cm}
   {HWS 2021}
  \end{center}
\end{titlepage} 

% no lets make some add some table of contents
%\tableofcontents
%\newpage

%\listofalgorithms

%\listoffigures

%\listoftables

% evntuelly you might add something like this
% \listtheorems{definition}
% \listtheorems{proposition}

\newpage


% okay, start new numbering ... here is where it really starts
\pagenumbering{arabic}

\section{What is the problem you are solving?}

This document represents the case study proposal for Team MINEheim (Group 1). After extensive research in different topic areas and comparing multiple data sets that might be relevant for such a student project, we decided that we would like to focus on the wine industry. In addition, every group member is interested in research questions regarding the mentioned industry and we definitely see a lot of potential for different data mining techniques to analyze our data set.

With the help of our data set and various data mining methods we want to objectively classify wine based on its distinct attributes. To go into more detail, we want to predict the quality of wine based on its components and features. The target variable is the wine quality. Our approach solves the following problem and leads to a valuable business case for target groups:

First of all, the prediction of wine quality based on its components is highly-valuable for wineries and large wine dealers. By following our approach, wineries and dealers can objectively determine the quality of their products which might lead to a higher market success. Moreover, our case study facilitates the valuing of wine without actually drinking it. In general, you would use experienced wine sommeliers to determine the quality of wine, but those are rare, require long training and increase the costs for product development. It is also worth mentioning that due to food regulations, wine ingredients are measured anyways. By predicting the wine quality with data mining algorithms, it’s possible to shorten the taste-testing procedure of experienced sommeliers and to save important financial resources. Our solution enables possible customers to recommend their wine to consumers and solves the weak spot that the whole wine industry heavily relies on the subjective taste of a few wine sommeliers.

\section{What data will you use?}
To solve the problem outlined above a publicly available data set on wine quality from \textit{data.world} [\url{https://data.world/uci/wine-quality}] will be used. The data set is related to red and white variants of the Portuguese wine “Vinho Verde”, a unique wine product from the northwest region of Portugal. The data was originally collected by an inter-professional organization called CVRVV between 2004 and 2007 for marketing and quality assurance purposes. Since the data is already gathered there are no additional steps necessary. 

Taking a closer look at the data set we can identify 13 features, twelve input variables and one output variable respectively. The input variables mainly represent the test results of physiochemical properties of each specific wine, e.g., pH-value, alcohol concentration, sulfates etc. These properties are measured in their respective measurement unit. Each wine is also classified by its type (red or white). The quality of the wine is represented by a score metric ranging from 0 to 10, with 0 meaning very bad and 10 referring to excellent. Each wine sample was evaluated with a sensory test (blind test) by at least three assessors and then graded. The final grade was calculated with the median of these tests. According to the data set description the classes are ordered but unbalanced.


\section{How will you solve the problem?}
\subsection{What preprocessing steps will be required?}
To prepare the data we received from data set to be useful for our different algorithms a couple of preprocessing
steps will be required. This includes the following:

\textbf{Under-/oversampling -- data balancing} In a first glance at the data we noticed that the class distribution is
unbalanced. There are more normal wines than great or bad ones. For that reason we have to decide what to do about it -- how many classes we want to predict (e.g., binary classification or three classes: bad, normal and good), and how we want to distribute the samples among the classes so that it is balanced (e.g., via under- or oversampling).

\textbf{Data analysis and inspection} In the next step we must explore whether the data set includes duplicates, null values or outliers. Additionally, we can analyze whether there is any correlation between different features in the data set. Furthermore, it needs to be evaluated if the introduction of additional features improves the classifier.

\textbf{Feature standardization of numerical values (normilaztion)} In order to have good results when building the classifiers we have to bring each numerical features into the same scale so one feature does not have a bigger impact on the outcome than others. For that reason we have do standardize or normalize the numerical features.

\subsection{Which algorithms do you plan to use?}
We plan on using six to seven different classifiers to solve the problem. Since we 
are trying to solve a classification task, the algorithms we plan on using are classification
algorithms.

Firstly, we intend to use \textbf{k-nearest neighbors (k-NN)} as a baseline
algorithm for our classification problem as k-NN is quite a simple algorithm.
Additionally, we want to use \textbf{decision trees} to try build a model to classify the
data. As an extension of decision trees we are also interested in using a \textbf{random forest}
to derive a classifier.
Furthermore, other classification algorithms that we want to use include a \textbf{Support Vector Machine (SVM)}
or \textbf{logistic regression} -- although logistic regression could only be used if we decide on
a binary classification problem (i.e., deciding between wines of good and bad quality).
Moreover, we want to build a \textbf{neural network} that can predict if a given wine is of good or bad quality.

Finally, we are interested in using \textbf{outlier detection / anomaly detection algorithms} to detect the few 
excellent or poor wines that are given in the data set.
Generally, we intend to use \textbf{feature selection} test for each algorithm if there are any features which are not relevent 
for classifying between good and bad wines to exclude them from the model. In addition to that we plan to include
\textbf{hyperparameter tuning} for the different algorithms to optimize the models.

\section{How will you measure success?}
As part of the evaluation the success will be measured with different suitable metrics. A classification model reveals data about correct and incorrect predictions which is summarized in a confusion matrix. This confusion matrix displays the differences between the predicted and true values of a specific use case within the visual representation of a matrix. Based on this matrix different evaluation metrics can be calculated. For the before described use case, the following evaluation metrics were chosen:
First of all, it is intended to calculate the \textbf{recall} of the model which calculates the ratio between the true positive and the total number of data sets. Secondly, the \textbf{precision} is chosen as a second evaluation metric. The precision defines the difference between the true positives and the number of the truly predicted values. Thirdly, these two evaluation metrics precision and recall are combined within the \textbf{$F_1-Score$} which mathematically represents the harmonic mean of the precision and recall. In addition, the \textbf{accuracy} as well as the \textbf{cross entropy} of the model will be considered. Lastly, the \textbf{importance} of each individual input parameter will be evaluated for each model. Each model is based on a specific machine learning algorithm. The outcome of the measurement of the importance might influence the improvement of the model.


\section{What do you expect your results to look like?}
We generally expect that there is a correlation between the make up of different wines and their taste (quality). Without analyzig the particular data set we found different sources that link for example, the ph-value of wine to whether it is sour or mild. Furthermore, attributes like alcohol percentage or sugar effect the sweetness of wine. Even though taste and quality might be subjective, for example sweeter wine might be generally more liked by a broader audience than bitter wine. That's why we expect to being able to predict the quality of different wines. Nonetheless, the precision of our model could be rather poor, just because of the fact that quality and taste are subjective. On the other hand the quality of wine must be influenced by its ingredients, because of that our results might be more precise than we initially expect.

%%% Un-Comment to use the bibliography
%\bibliographystyle{plain}
%\bibliography{thesis-ref.bib}


%\appendix


%\newpage


%\pagestyle{empty}


%\section*{Ehrenw\"ortliche Erkl\"arung}
%Ich versichere, dass ich die beiliegende Master-/Bachelorarbeit ohne Hilfe Dritter
%und ohne Benutzung anderer als der angegebenen Quellen und Hilfsmittel
%angefertigt und die den benutzten Quellen w\"ortlich oder inhaltlich
%entnommenen Stellen als solche kenntlich gemacht habe. Diese Arbeit
%hat in gleicher oder \"ahnlicher Form noch keiner Pr\"ufungsbeh\"orde
%vorgelegen. Ich bin mir bewusst, dass eine falsche Er- kl\"arung rechtliche Folgen haben
%wird.
%\\
%\\

%\noindent
%Mannheim, den 31.08.2014 \hspace{4cm} Unterschrift

\end{document}
